\vspace{-0.25em}\thetitle

### 2009-07-29 paper.tex
Simplified prediction stats table.
Added plot for success rates.

As better point-measure of the quality of predictors, we propose the maximum vertical distance between its p-value \caps{CDF} and the ideal.
This is equivalent to choosing the worst possible predetermined significance level for each predictor and evaluating it at that level.
Under this measure, predictors cannot ``hide'' their errors by shifting them around the p-value range.
The maximum vertical difference from the ideal for each predictor is shown in \Figure{cdf} with vertical bars.
The number next to each bar is the length of this distance:
this is the the overall error rate of the predictor.

\hline
\textbf{Trace} &
\textbf{Predictor} &
\textbf{0.01-error} &
\textbf{0.05-error} &
\textbf{max-error} \\
\hline

\end{tabular}
\caption{Error rates for size and interval predictions for all traces.}
\tab{traces}
\end{center}
\vspace{-2em}
\end{table*}

>>>>

As better point-measure of the quality of predictors, we propose the maximum vertical distance between its p-value \caps{CDF} and the ideal.
This is equivalent to choosing the worst possible predetermined significance level for each predictor and evaluating it at that level.
Under this measure, predictors cannot ``hide'' their errors by shifting them around the p-value range.
The maximum vertical difference from the ideal for each predictor is shown in \Figure{cdf} with vertical bars.
This is the the overall error rate of the predictor.
The success rate is the complement of the error rate.
\Figure{success-rates} shows the success rates of various predictions across the six data sets.

\begin{figure}[!b]
\vspace{-2em}
\begin{center}
\includegraphics[width=3.5in]{pred_stats}
\caption{Success rates of various prediction methods.}
\fig{success-rates}
\end{center}
\vspace{-1em}
\end{figure}

% \begin{table}[b]
% \begin{center}
% \small
% \begin{tabular}{|c|c|c|c|c|c|c|}
% \hline
% &
% \multicolumn{2}{c|}{\textbf{Predicted}} &
% \multicolumn{2}{c|}{\textbf{Self}} &
% \multicolumn{2}{c|}{\textbf{Mean}} \\
% \hline
% \textbf{Trace} &
% \textbf{size} & \textbf{ival} &
% \textbf{size} & \textbf{ival} &
% \textbf{size} & \textbf{ival} \\
% \hline
% \input{pred_stats}
% \hline
% \end{tabular}
% \caption{Error rates for size and interval predictions.}
% \tab{error-rates}
% \end{center}
% \vspace{-1em}
% \end{table}
